### 2019-05-19 README.Rmd
Adds vis_value to visualise all values in dataset
* Updates error message when functions need all numeric data. This is for vis_cor and vis_value.
* use dplyr::n()
* use `guess_integer = TRUE` for `guess_type`.
* Flesh out documentation for vis_value

>>>>

## Using `vis_value`

`vis_value()` visualises the values of your data on a 0 to 1 scale.

```{r vis-value}
vis_value(airquality)
```

It only works on numeric data, so you might get strange results if you are using   factors:

```{r iris-error, eval = FALSE}
library(ggplot2)
vis_value(iris)
```

```
data input can only contain numeric values, please subset the data to the numeric values you would like. dplyr::select_if(data, is.numeric) can be helpful here!
```

So you might need to subset the data beforehand like so:

```{r iris-error-fix}
library(dplyr)

iris %>%
  select_if(is.numeric) %>%
  vis_value()
```
